### 2019-02-13 sections/contributions.tex
Added old list-style contributions to current contributions write-up

% \paragraph{Contributions}

@@

>>>>

\subsection{Contributions}

@@

\begin{itemize*}
  \item A calculus to model workflows, which can be used in a modular way and are driven by user inputs.\\
  \item Embed this calculus in a simply typed $\lambda$-calculus.\\
  \item Its operational semantics, presented and defined in a layered way.\\
  \item Semantic observations on the calculus which can be used to:\\
  \begin{itemize*}
    \item calculate stuck configurations,\\
    \item associate a value with a task,\\
    \item draw a user interface (\UI) for a task,\\
    \item calculate input possibilities for the user.\\
  \end{itemize*}
  \item A clear separation between \TOP principles and general purpose programming constructs.\\
\end{itemize*}
